---
title: "Fuzzy action: pilot"
output: html_document
---


```{r setup, include = FALSE, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(fig.width=8, fig.height=6, 
                      echo=FALSE, warning=FALSE, message=FALSE)
require(dplyr)
require(ggplot2)
require(reshape2)

```


## Experiment

9 participants recruited via MTurk on March 25 2016. Paid 0.60 US-Dollar compensation.

Each participant interpreted 7 descriptions each for 4 scenarios by selection one of 15 intervals of values (from previous experiment by Ciyang and Michael). Scenarios were presented at random. Then all 7 descriptions for that scenario at random.

Scenarios:

1. male NBA basketball player: *tall* vs *short*
2. female gymnast: *tall* vs *short*
3. blockbuster movie: *long* vs *short*
4. radio song: *long* vs *short*

Descriptions: 

1. "Q", 
2. "not-P ", 
3. "neither Q nor not-P",
4. "neither P nor Q", 
5. "neither P nor not-Q",
6. "not-Q", 
7. "P"

Here, "P" is either *tall* or *long* and "Q" is *short*



## Motivation

Is there a coherent rank order among these descriptions? What is it?

## Results

Mean interval choices:

```{r, echo = FALSE}
d = read.csv('data.csv') %>%
  mutate(id = as.numeric(factor(id)),
         expressionLabel = factor(expressionLabel, ordered = TRUE, 
                                  levels = c("Q", "not-P ", "neither Q nor not-P",
                                             "neither P nor Q", "neither P nor not-Q", "not-Q", "P"))) %>% 
  group_by(id, scenarioLabel) %>%
  mutate(rank = rank(answer))

p = ggplot(d, aes(y = answer, x = factor(expressionLabel))) + geom_boxplot() + facet_grid(scenarioLabel ~ .) + coord_flip()
show(p)

```

Rank of interval choices against expected rank order by participants:

```{r}
q = ggplot(d, aes(x = expressionLabel, y = rank)) + geom_point() + facet_grid(id ~ scenarioLabel) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
show(q)
```
