---
title: "Fuzzy action: 2nd pilot "
output: html_document
---


```{r setup, include = FALSE, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(fig.width=8, fig.height=8, 
                      echo=FALSE, warning=FALSE, message=FALSE)
require(dplyr)
require(ggplot2)
require(reshape2)

```

```{r}
d = read.csv('data.csv')
d = droplevels(subset(d, d$id != "debug5B1ZMX:debugAJ5FRP"))
d = subset(d, RT >= 3500)
nr_participants_initial = nlevels(factor(d$id))
```



## Experiment



`r nr_participants_initial` participants were recruited via MTurk on March 30 2016 and paid 0.35 US-Dollar compensation.

Each participant interpreted 1 description for 6 scenarios by adjusting a slider bar. They also rated the naturalness of the description on a 7-point Likert scale. Scenarios and descriptions were presented at random. No two scenarios or descriptions were shown twice. 

Scenarios:

1. US male: *tall* vs *short*
2. bath: *hot* vs *cold*
3. movie: *long* vs *short*
4. laptop: *expensive* vs *cheap*
5. band: *full* vs *empty*
6. car: *fast* vs *slow*

Descriptions: 

1. "Q", 
2. "not-P ", 
3. "neither Q nor not-P",
4. "neither P nor Q", 
5. "neither P nor not-Q",
6. "not-Q", 
7. "P"
8. "P and not-P"
9. "Q and not-Q"

Here, "P" is either *tall* and "Q" is *short* for scenario "US male".

## Questions of interest

1. Is there a coherent rank order among these descriptions? What is it?
    - e.g., is "not-Q" interpreted as higher than "neither P nor Q"?
2. Is there a correlation between the naturalness ratings and the variance in interpretation (by-scenario & by-description)?
3. Is there lower variance in interpretation for "P and not-P" vs "neither P nor not P"?
4. Does predicate type (stage-level vs. individual-level) have an effect on naturalness ratings? Here, we care especially for borderline contradictions.

## Exclude some participants

```{r}

d = droplevels(filter(d, ! language %in% c("bulgarian", "Chinese", "Hindi") ))
nr_excluded_for_language = nr_participants_initial - nlevels(factor(d$id)) 

d$workerID = unlist(sapply(1:nrow(d), function(i) strsplit(as.character(d$id[i]), ":")[[1]][1]))
d$assignmentID = unlist(sapply(1:nrow(d), function(i) strsplit(as.character(d$id[i]), ":")[[1]][2]))

```

We exclude `r nr_excluded_for_language` participants as not being self-reported native English speakers. We did not have any double takers, so we have a total of `r nr_participants_initial - nr_excluded_for_language` participants. This gives us an expectation of `r round((nr_participants_initial - nr_excluded_for_language) / 9,2)` answers per scenario-description pair.

## Vizualize results

Interpretations:

```{r, echo = FALSE}
d = d %>%
  mutate(id = as.numeric(factor(id)),
         expressionLabel = factor(expressionLabel, ordered = TRUE, 
                                  levels = c("Q", 
                                             "not-P ", 
                                             "Q and not-Q", 
                                             "neither Q nor not-Q", 
                                             "neither P nor Q", 
                                             "neither P nor not-P", 
                                             "P and not-P",
                                             "not-Q", 
                                             "P")),
         answerRescaled = 0) %>% 
  group_by(id, scenarioLabel) %>%
  mutate(rank = rank(answer))

interpretation_plot = ggplot(d, aes(y = answer, x = factor(expressionLabel))) + 
  geom_boxplot() + 
  facet_grid(scenarioLabel ~ ., scales = "free") + 
  coord_flip() + xlab("expression") + ylab("interpretation (rescaled)")
show(interpretation_plot)

```

Ranks of means of interpretations, plotted against "expectation":

```{r}
mean_interpretation_ranks = d %>% group_by(scenarioLabel, expressionLabel) %>%
  summarize(mean_interpretation = mean(answer)) %>%
  group_by(scenarioLabel) %>%
  mutate(rank_of_means = rank(mean_interpretation))

mean_interpretation_ranks_plot = ggplot(mean_interpretation_ranks,
                                        aes(x = expressionLabel,
                                            y = rank_of_means)) +
  geom_point() + facet_wrap(~ scenarioLabel, nrow = 2) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + geom_abline(intercept = 0, color = "gray")
show(mean_interpretation_ranks_plot)
```


Rank order of means of interpretations, by scenario:

```{r}
mean_interpretation_ranks_plot_text = ggplot(mean_interpretation_ranks,
                                             aes(x = rank_of_means,
                                                 y = 1,
                                                 label = expressionLabel,
                                                 color = expressionLabel)) +
  geom_text() + facet_wrap(~ scenarioLabel, nrow = 2) + coord_flip()
show(mean_interpretation_ranks_plot_text)
```


Naturalness ratings:

```{r}
naturalness_plot = ggplot(d, aes(y = naturalness, x = factor(expressionLabel))) + 
  geom_boxplot() + 
  facet_grid(scenarioLabel ~ .) + 
  coord_flip() + xlab("expression") + ylab("naturalness")
show(naturalness_plot)
```

Rank order of naturalness ratings:

```{r}
mean_naturalness_ranks = d %>% group_by(scenarioLabel, expressionLabel) %>%
  summarize(mean_naturalness = mean(naturalness)) %>%
  group_by(scenarioLabel) %>%
  mutate(rank_of_naturalness = rank(mean_naturalness, ties.method = "average"))

mean_naturalness_ranks_plot_text = ggplot(mean_naturalness_ranks,
                                             aes(x = rank_of_naturalness,
                                                 y = 1,
                                                 label = expressionLabel,
                                                 color = expressionLabel)) +
  geom_text() + facet_wrap(~ scenarioLabel, nrow = 2) + coord_flip()
show(mean_naturalness_ranks_plot_text)

```



Variance in interpretations against naturalness:

```{r}
correlation_data = d %>% group_by(scenarioLabel, expressionLabel, predicateType) %>%
  summarize(mean_naturalness = mean(naturalness),
            variance_interpretation = var(answer))

correlation_plot = ggplot(correlation_data, aes(x = mean_naturalness, y = variance_interpretation)) +
  geom_point()
show(correlation_plot)
```

