---
title: "Fuzzy action: 4th pilot "
output: html_document
---


```{r setup, include = FALSE, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(fig.width=8, fig.height=8, 
                      echo=FALSE, warning=FALSE, message=FALSE)
require(dplyr)
require(ggplot2)
require(reshape2)

```

```{r}
d4 = read.csv('data.csv')
nr_participants_initial = nlevels(factor(d4$id))
```



## Experiment



`r nr_participants_initial` participants were recruited via MTurk on April 6 2016 and paid 1 US-Dollar compensation.

Each participant interpreted 7 descriptions for 6 scenarios by by selecting a point on a 10-point Likert scale. Scenarios and description order was randomized. 

Scenarios:

1. US male: *tall* vs *short*
2. bath: *hot* vs *cold*
3. movie: *long* vs *short*
4. laptop: *expensive* vs *cheap*
5. band: *full* vs *empty*
6. car: *fast* vs *slow*

Descriptions (*no borderline contradictions*): 

1. "Q", 
2. "not-P ", 
3. "neither Q nor not-P",
4. "neither P nor Q", 
5. "neither P nor not-Q",
6. "not-Q", 
7. "P"

Here, "P" is either *tall* and "Q" is *short* for scenario "US male".

## Questions of interest

1. Is there a coherent rank order among these descriptions? What is it?
    - e.g., is "not-Q" interpreted as higher than "neither P nor Q"?

## Exclude some participants

```{r}

d4 = droplevels(filter(d4, ! language %in% c("chinese", "Chinese", "english, vietnamese", "Spanish", "Telugu") ))
nr_excluded_for_language = nr_participants_initial - nlevels(factor(d4$id)) 

d4$workerID = unlist(sapply(1:nrow(d4), function(i) strsplit(as.character(d4$id[i]), ":")[[1]][1]))
d4$assignmentID = unlist(sapply(1:nrow(d4), function(i) strsplit(as.character(d4$id[i]), ":")[[1]][2]))

```

We exclude `r nr_excluded_for_language` participants as not being self-reported native English speakers. We have a total of `r nr_participants_initial - nr_excluded_for_language` participants. Since every participant interpreted every description for every scenario, that is then also the exact count of data-points for all conditions of interest.

```{r}

## data prep



### reshuffle results
A1 = melt(d4, id.vars = c("id", "scenarioLabel", "expressionLabel1"), measure.vars = c("answer1")) %>%
  rename(expressionLabel = expressionLabel1)
A2 = melt(d4, id.vars = c("id", "scenarioLabel", "expressionLabel2"), measure.vars = c("answer2")) %>%
  rename(expressionLabel = expressionLabel2)
A3 = melt(d4, id.vars = c("id", "scenarioLabel", "expressionLabel3"), measure.vars = c("answer3")) %>%
  rename(expressionLabel = expressionLabel3)
A4 = melt(d4, id.vars = c("id", "scenarioLabel", "expressionLabel4"), measure.vars = c("answer4")) %>%
  rename(expressionLabel = expressionLabel4)
A5 = melt(d4, id.vars = c("id", "scenarioLabel", "expressionLabel5"), measure.vars = c("answer5")) %>%
  rename(expressionLabel = expressionLabel5)
A6 = melt(d4, id.vars = c("id", "scenarioLabel", "expressionLabel6"), measure.vars = c("answer6")) %>%
  rename(expressionLabel = expressionLabel6)
A7 = melt(d4, id.vars = c("id", "scenarioLabel", "expressionLabel7"), measure.vars = c("answer7")) %>%
  rename(expressionLabel = expressionLabel7)

answers = rbind(A1, A2, A3, A4, A5, A6, A7) %>%
  mutate(id = as.numeric(factor(id)),
         expressionLabel = factor(expressionLabel, ordered = TRUE, 
                                  levels = c("Q", 
                                             "not-P ", 
                                             "neither Q nor not-Q", 
                                             "neither P nor Q", 
                                             "neither P nor not-P", 
                                             "not-Q", 
                                             "P"))) %>% 
  group_by(id, scenarioLabel) %>%
  mutate(rank = rank(value))
```

# Visualize data

The number of Likert degrees chosen per scenario and description:

```{r}

bar_plot = ggplot(answers, aes(x = value)) + geom_bar() + facet_grid(scenarioLabel ~ expressionLabel)
show(bar_plot)

```

```{r}

box_plot = ggplot(answers, aes(x = expressionLabel, y = value)) + geom_boxplot() + facet_grid(scenarioLabel ~ .) + coord_flip()
show(box_plot)

```


